Zohmg---a large scale data store for aggregated time-series-based data. [DRAFT]

### 2009-08-12 doc/report/msc-report.tex

\documentclass[a4paper,10pt]{report}
\usepackage{graphicx}
\usepackage{listings}

\author{Per Andersson, Fredrik M{\"o}llerstrand}
\title{Zohmg---a large scale data store for aggregated time-series-based
data. [DRAFT]}

\begin{document}
\maketitle

@@

\noindent Per Andersson and Fredrik M{\"o}llerstrand both study Computer Science
at Chalmers University of Technology. This report is part of their master thesis
degree. The work was performed at Last.fm's office in London during spring 2009.

The authors would like to specially thank the supervisors---David Sands at
Chalmers and Johan Oskarsson and Martin Dittus at Last.fm---for their help and
support.

The authors would also like to thank the staff at Last.fm and their family and
friends for moral support before, during, and after the thesis work.

\pagebreak
\phantom{ }
\pagebreak

\tableofcontents
\vfill
\pagebreak

>>>>

\documentclass[a4paper,10pt]{report}
\usepackage{graphicx}
\usepackage{listings}
\usepackage{chngpage}

\begin{document}

\newpage
\changepage{60mm}{}{}{-39mm}{}{-45mm}{}{}{}

\renewcommand\thepage{}

\begin{center}
    \includegraphics{chalmers-header.eps}
\end{center}

\vspace{60mm}

\begin{adjustwidth}[]{20mm}{-40mm}
    {\huge \textbf{Zohmg---a large scale data store for \\
    aggregated time-series-based data. [DRAFT]}}

    \vspace{6pt}

    \noindent {\large \textit{Master of Science Thesis}}

    \vspace{36pt}

    \noindent {\Large \textbf{PER ANDERSSON}}

    \noindent {\Large \textbf{FREDRIK M{\"O}LLERSTRAND}}

    \vfill

    \noindent Department of Computer Science and Engineering

    \noindent CHALMERS UNIVERSITY OF TECHNOLOGY

    \noindent G{\"o}teborg, Sweden, 2009
\end{adjustwidth}

\newpage
\renewcommand\thepage{\arabic{page}}
\changepage{-60mm}{}{}{39mm}{}{47mm}{}{}{}

\setcounter{page}{1}

\noindent The Author grants to Chalmers University of Technology and University
of Gothenburg the non-exclusive right to publish the Work electronically and in
a non-commercial purpose make it accessible on the Internet.

\noindent The Author warrants that he/she is the author to the Work, and
warrants that the Work does not contain text, pictures or other material that
violates copyright law.

\noindent The Author shall, when transferring the rights of the Work to a third
party (for example a publisher or a company), acknowledge the third party about
this agreement. If the Author has signed a copyright agreement with a third
party regarding the Work, the Author warrants hereby that he/she has obtained
any necessary permission from this third party to let Chalmers University of
Technology and University of Gothenburg store the Work electronically and make
it accessible on the Internet.

\vspace{64pt}

\noindent Zohmg---a large scale data store for aggregated time-series-based
data.

\vspace{24pt}

\noindent PER ANDERSSON

\noindent FREDRIK M{\"O}LLERSTRAND

\noindent {\copyright} PER ANDERSSON, August 2009

\noindent {\copyright} FREDRIK M{\"O}LLERSTRAND, August 2009

\noindent Examiner: DAVID SANDS

\vspace{72pt}

\noindent Department of Computer Science and Engineering

\noindent Chalmers University of Technology

\noindent SE-412 96 Göteborg

\noindent Sweden

\noindent Telephone + 46 (0)31-772 1000

\vfill

\noindent Department of Computer Science and Engineering

\noindent G{\"o}teborg, Sweden, 2009

@@

\noindent Per Andersson and Fredrik M{\"o}llerstrand both study Computer
Science at Chalmers University of Technology in Gothenburg, Sweden. This thesis
is part of their master's degree. The work was performed at Last.fm's
office in London during spring 2009.

The authors would like to especially thank the supervisors---David Sands at
Chalmers and Johan Oskarsson and Martin Dittus at Last.fm---for their help and
support.

Per would like to especially thank Hedvig Kamp for help and guidance with the
thesis and general matters in life.

The authors would also like to thank their respective families and friends, and
the staff at Last.fm for their moral support before, during, and after the
thesis work.

\vspace{24pt}

\noindent \textbf{Acknowledgements}
\vspace{12pt}

\noindent Figure 2.1 is Copyright {\copyright} 2008 Robert Burrell Donkin,
licensed under Creative Commons Attribution 3.0 License.

\pagebreak
This page is intentionally left blank.
\pagebreak

\tableofcontents
\vfill

\begin{minipage}{116mm}
    \listoffigures
\end{minipage}

\begin{minipage}{116mm}
    \listoftables
\end{minipage}
